\medskip

\hspace{10pt}Natural Language Processing (NLP) is a branch of artificial intelligence (AI) utilized to analyze and interpret written and verbal human language. The primary objective is to design programs that can generate and comprehend natural language, enabling people to communicate with computers and have computers analyze their needs.\cite{NLPFrank} Machine learning is finding more and more applications in data analytics, such as the creation of chatbots that can mimic human user discussions by extracting relevant insights from massive databases. \cite{NLPFrank}

\medskip

\hspace{10pt}One prominent application of NLP is the development of chatbots. Chatbots utilize NLP to facilitate human-like interactions between computers and users, offering a wide range of functionalities from customer service to personal assistance. In this project, the primary function of the chatbot is spell correction. Spell correction tools are essential for enhancing written communication by automatically identifying and rectifying spelling errors. For non-native English learners, spell correction tools serve as a valuable aid, helping them to learn and use new vocabulary accurately. This chatbot will not only help users recognize and correct their spelling mistakes but also enhance their overall learning experience by reinforcing the correct spelling of words.

\medskip

\hspace{10pt}The primary objective of this project is to apply the concepts and techniques learned in NLP to develop a practical tool that assists non-native English learners in improving their vocabulary. This chatbot utilize various NLP concepts such as tokenization, vectorization, and neural networks to detect, correct spelling errors, and provide real-time feedback to users.